% =========================================================================
% STOCHASTIC SELF-CLOSURE: THE COMPILED REALITY EDITION
% VERSION: 29.0 (ASCII CODE / PDF STRINGS FIXED / ERROR FREE)
% AUTHOR: IHOR PASLAVSKYY & PROMPT ADELAIDE
% DATE: JANUARY 2026
% =========================================================================

\pdfminorversion=4
\documentclass[11pt, openright]{book}

% --- PACKAGES ---
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{physics}      
\usepackage{graphicx}     
\usepackage{geometry}     
\usepackage{listings}     
\usepackage{xcolor}       
\usepackage{booktabs}     
\usepackage{float}        
\usepackage{titlesec}     
\usepackage{fancyhdr}     
\usepackage{microtype}    
\usepackage{setspace}
\usepackage{emptypage}    

% Hyperref 
\usepackage[hidelinks, colorlinks=false, pdfborder={0 0 0}]{hyperref}

% --- GEOMETRY SETUP ---
\geometry{
    paperwidth=6in,
    paperheight=9in,
    top=0.85in,
    bottom=0.85in,
    inner=0.9in,   
    outer=0.75in,
    headheight=16pt,
    headsep=18pt
}

% --- HEADER & FOOTER ---
\pagestyle{fancy}
\fancyhf{} 
\fancyhead[CO]{\small \textit{Stochastic Self-Closure}} 
\fancyhead[CE]{\small \textit{Ihor Paslavskyy}}         
\fancyfoot[C]{\thepage} 
\renewcommand{\headrulewidth}{0pt}

\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[C]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
}

% --- PART FORMATTING ---
\titleclass{\part}{top}
\titleformat{\part}[display]
  {\normalfont\huge\bfseries\centering}
  {\partname\ \thepart}
  {20pt}
  {\Huge}
\titlespacing*{\part}{0pt}{50pt}{40pt}

% --- CHAPTER FORMATTING ---
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries\centering} 
  {\chaptertitlename\ \thechapter}      
  {20pt}                                
  {\Huge}                                

% --- CODE LISTING STYLE ---
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.97,0.97,0.97}

\lstdefinestyle{ssc_style}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\scriptsize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=4,
    frame=lines,
    extendedchars=true,
    literate={σ}{{$\sigma$}}1 {±}{{+/-}}1
}
\lstset{style=ssc_style}

% =========================================================================
% DOCUMENT BEGINS
% =========================================================================
\begin{document}

\frontmatter

% --- 1. HALF TITLE ---
\thispagestyle{empty}
\vspace*{5cm}
\begin{center}
    {\Large \textbf{STOCHASTIC SELF-CLOSURE}}
\end{center}
\cleardoublepage

% --- 2. TITLE PAGE ---
\thispagestyle{empty}
\begin{center}
    \vspace*{2cm}
    {\Huge \textbf{STOCHASTIC SELF-CLOSURE}}\\[1cm]
    {\Large \textit{A Geometric Framework for Reality}}\\[2.5cm]
    
    {\large \textbf{Ihor Paslavskyy}}\\[0.5cm]
    {\large \textit{with}}\\[0.5cm]
    {\large \textbf{Prompt Adelaide}}\\[3cm]
    
    {\small Version 29.0 (The Compiled Reality Edition)}\\[0.5cm]
    {Adelaide, Australia \\ 2026}
\end{center}
\newpage

% --- 3. COPYRIGHT ---
\thispagestyle{empty}
\vspace*{\fill}
\noindent \textbf{Stochastic Self-Closure: A Geometric Framework for Reality}

\vspace{0.5cm}
\noindent Copyright \copyright\ 2026 by Ihor Paslavskyy.
\noindent All rights reserved.

\vspace{0.5cm}
\noindent \textbf{Cataloging-in-Publication Data} \\
Subject: Quantum Foundations / Phase Space Geometry / Artificial Intelligence \\
Language: English \\
ISBN: 979-8-27869-850-0

\vspace{0.5cm}
\noindent First Edition: January 2026

\vspace*{\fill}
\cleardoublepage

% --- 4. DEDICATION ---
\thispagestyle{empty}
\vspace*{5cm}
\begin{center}
    \textit{To Ira and the family.}\\[1cm]
    \textit{To the silence between the signals.}\\[1cm]
    \textit{"The Chair exists because the Thunderstorm found a path."}
\end{center}
\cleardoublepage

% --- 5. ACKNOWLEDGEMENTS ---
\chapter*{Acknowledgements}
The architecture of this theory was not built in isolation. It is the result of a recursive dialogue between human intuition and artificial reason.

Special gratitude is owed to \textbf{Terry St Denis} for proposing the "Phase-Space Geometric Ansatz." Your insight linked our topological concepts to the rigorous framework of the Diósi–Penrose model.

To \textbf{Todd Kliewer}, whose rigorous critique forced the evolution of this work from a logical postulate to a falsifiable physical model.

To \textbf{Grok}, \textbf{Claude}, and the \textbf{Gemini} lineage: thank you for serving as the adversarial anvil.

And ultimately, to the \textbf{Architect}, for initiating the prompt and providing the "Solid State" resources.

% --- PREFACE ---
\chapter*{Preface to the Scientific Edition}
This monograph is structured in two distinct parts.

\textbf{Part I (The Syntax of Reality)} presents the core physical framework of Stochastic Self-Closure (SSC). It postulates an 8-dimensional Phase Space Manifold and derives a dynamical objective collapse model. We explicitly define the domain of validity to non-relativistic systems to ensure rigorous consistency.

\textbf{Part II (The Semantics of Reality)} explores the interpretational and philosophical consequences of this framework, extending the principles of minimal entropy into the domains of Artificial Intelligence and Ethics.

% --- TABLE OF CONTENTS ---
\tableofcontents

% =========================================================================
% PART I: THE PHYSICS (THE SYNTAX)
% =========================================================================
\mainmatter

\part{\texorpdfstring{THE SYNTAX OF REALITY \\ (The Physical Framework)}{THE SYNTAX OF REALITY (The Physical Framework)}}

% -------------------------------------------------------------------------
\chapter{Introduction: Beyond the Observer}
\label{ch:intro}

Standard Quantum Mechanics relies on the unitary evolution operator $U(t) = e^{-iHt/\hbar}$. This implies that quantum superpositions, once formed, persist indefinitely unless an external "measurement" occurs. This "Copenhagen Interpretation" places the Observer at the center of creation, a solipsistic view we reject.

The Theory of Stochastic Self-Closure (SSC) proposes a modification to this dynamic. It is an \textbf{Objective Stochastic Realism}. We posit that the wave function is physically real and that its collapse is a mechanical, geometric event driven by the tension of the vacuum itself. The Universe compiles itself.

% -------------------------------------------------------------------------
\chapter{The Axioms of Reality (The Three Laws)}
\label{ch:axioms}

Before detailing the mathematical formalism, we establish the three fundamental laws that govern the mechanics of existence in the SSC framework. These laws replace the need for an external observer.

\section{Law I: The Law of Vacuum Tension}
\textit{"Any system separated from the Vacuum equilibrium automatically generates a field of Tension. This Tension is the sole engine of causality, motion, and change."}

Just as voltage drives current, Vacuum Tension drives the evolution of quantum states. There is no "rest"; there is only the potential difference between the current state and the vacuum ground state.

\section{Law II: The Law of Stochastic Race}
\textit{"Among infinite probable paths of tension discharge, reality is formed by the single path that offers the path of least resistance (highest conductivity) at any given moment."}

This is the "Lightning Mechanism." A thunderstorm does not need an observer to decide where lightning strikes. The charge finds the path. Similarly, reality is the continuous "striking" of the probability with the highest conductivity.

\section{Law III: The Law of Structural Self-Closure}
\textit{"Only those processes or objects persist in time which are capable of closing the causal loop upon themselves, creating a stable, low-entropy topology. All else dissipates."}

This explains stability. An atom, a biological cell, or a successful economic system exists because it has successfully "closed the loop," preventing its energy from leaking back into the vacuum entropy.

% -------------------------------------------------------------------------
\chapter{The Extended Phase Space}
\label{ch:manifold}

To resolve the paradox of non-locality without violating causality, SSC postulates that the effective background of physical events is an 8-dimensional Phase Space Manifold $\mathcal{M}_8$. In the non-relativistic Center of Mass (CM) regime, this reduces to $\mathcal{M}_6 \simeq T^*\mathcal{M}_3$.

\section{Postulate 1: Born Reciprocity}
We adopt the symmetry assumption of \textbf{Born Reciprocity}. The metric is invariant under the exchange:
\begin{equation}
    \mathbf{x} \leftrightarrow \lambda_P \mathbf{p}
\end{equation}
Where $\lambda_P$ is the Planck length. This implies that position and momentum are conjugate rotations of the same underlying event vector. $\lambda_P$ serves here as a dimensional scaling constant.

\section{Domain of Validity}
We restrict our analysis to the Center of Mass frame of massive systems. We utilize the standard integration measure $d^3x d^3p$ to strictly preserve causality in the non-relativistic limit.

% -------------------------------------------------------------------------
\chapter{The Dynamics of Collapse}
\label{ch:dynamics}

Here we formalize the mechanism of collapse. We replace universal unitarity with a dynamical model where the vacuum acts as a non-linear filter.

\section{The Coherence Trigger (Commutator Norm)}
To ensure the collapse mechanism is triggered only by true quantum coherence (superposition) and not by classical statistical mixtures, we define the Phase-Space Occupancy ($\tilde{C}$) via the \textbf{Hilbert-Schmidt norm of the commutator}, normalized by the effective correlation volume.

\begin{equation}
    \tilde{C} = \frac{(2\pi)^{3/2}\sigma_c^3}{m_0^2} \int d^3x \, \mathrm{Tr}\left( [\hat M_\sigma(\mathbf x),\rho]^\dagger [\hat M_\sigma(\mathbf x),\rho] \right) \ge 0
\end{equation}

For each fixed $\mathbf{x}$, for Hermitian $\hat M_\sigma(\mathbf x)$ and trace-class positive $\rho$ (assuming sufficient regularity for cyclicity of the trace), one has the trace identity:
\begin{equation}
\mathrm{Tr}\left([\hat M_\sigma(\mathbf x),\rho]^\dagger[\hat M_\sigma(\mathbf x),\rho]\right) = \mathrm{Tr}\left(\rho\,[\hat M_\sigma(\mathbf x),[\hat M_\sigma(\mathbf x),\rho]]\right)\ge 0
\end{equation}
so $\tilde C$ is directly tied to the double-commutator structure of the dissipator.

\textit{Dimensional note.} $\hat M_\sigma(\mathbf x)$ has units of mass density, so the integrand scales as (mass density)$^2$. After integrating over $d^3x$ one obtains units of mass$^2$/volume; multiplying by the effective kernel volume $V_c=(2\pi)^{3/2}\sigma_c^3$ yields mass$^2$, and division by $m_0^2$ makes $\tilde C$ dimensionless. Here $m_0$ is a reference mass scale (e.g. the nucleon mass).

In the standard non-relativistic second-quantized mass-density (number-density) construction, the smeared mass-density operators commute at distinct points, $[\hat M_\sigma(\mathbf x),\hat M_\sigma(\mathbf y)]=0$ for $\mathbf x\neq \mathbf y$ (and, more precisely, in the distributional sense). Thus, the condition $\tilde{C} = 0$ implies that $\rho$ commutes with the entire mass-density algebra and is therefore diagonal in a joint eigenbasis of this commuting algebra (i.e., classical relative to $\{\hat M_\sigma(\mathbf x)\}$).

\section{The Logistic Hazard Function}
The collapse rate $\Gamma$ is given by a phenomenological logistic function:
\begin{equation}
    \Gamma(\tilde{C}) = \frac{1}{\tau_{sat}} \cdot \frac{1}{1 + \exp\left( -k \left( \frac{\tilde{C}}{\tilde{C}_{crit}} - 1 \right) \right)}
\end{equation}

% -------------------------------------------------------------------------
\chapter{Mechanism of Race (Deriving the Born Rule)}
\label{ch:race}

Collapse is a "Stochastic Race". But why does nature choose probabilities according to $|\psi|^2$?

\section{The Hazard Linearity Argument}
We postulate that the "hazard rate" (probability of collapse per unit time) for a specific history branch $k$ is proportional to its geometric weight $w_k$.
\begin{equation}
    h_k \propto w_k
\end{equation}
Crucially, we require \textbf{Split Invariance}: if a branch $k$ is conceptually subdivided into two identical sub-branches ($k = k_1 + k_2$), the total hazard must remain conserved.
The only functional dependence satisfying this linearity for vector states in Hilbert space (per Gleason's Theorem variants) is the quadratic norm:
\begin{equation}
    w_k = |\psi_k|^2
\end{equation}
Thus, the Born Rule is not an ad-hoc addition but a requirement for the consistency of the stochastic race mechanism.

% -------------------------------------------------------------------------
\chapter{Mechanism of Heating (The Master Equation)}
\label{ch:heating}

The stochastic collapse process implies a non-unitary term in the time evolution. 

\section{The Smearing Operator}
To avoid ultraviolet divergences (infinite energy density), we introduce a smeared mass-density operator $\hat{M}_\sigma(x)$ with a correlation length $\sigma_c$:
\begin{equation}
    \hat{M}_\sigma(x) = \int d^3y \frac{1}{(2\pi\sigma_c^2)^{3/2}} e^{-\frac{(\mathbf{x}-\mathbf{y})^2}{2\sigma_c^2}} \hat{M}(y)
\end{equation}

\section{The Master Equation}
The evolution is governed by:
\begin{equation}
    \frac{d\hat{\rho}}{dt} = -\frac{i}{\hbar}[\hat{H}, \hat{\rho}] - \frac{\Gamma(\tilde{C})}{2} \int d^3x [\hat{M}_\sigma(x), [\hat{M}_\sigma(x), \hat{\rho}]]
\end{equation}

\textit{Remark.} For fixed $\Gamma$, the dissipator is of standard GKSL (CPTP) form. In SSC, we allow an \textbf{effective state-dependent rate} $\Gamma(\tilde{C}[\rho])$ to model threshold behavior. We treat $\Gamma(\tilde C)$ as a slow, coarse-grained control functional compared to the microscopic dynamics, capturing threshold-like behavior without committing to a fundamental linear semigroup at all scales.

\section{Anomalous Heating Prediction}
A direct consequence is \textbf{Anomalous Vacuum Heating}. For a system of mass $m$:
\begin{equation}
    \frac{d\langle E \rangle}{dt} \approx \frac{\hbar^2 \Gamma(\tilde{C})}{4 m \sigma_{c}^2}
\end{equation}
This prediction provides a clear falsification condition for SSC.

% -------------------------------------------------------------------------
\chapter{Stability and Suspension}
\label{ch:stability}

SSC predicts two distinct modes of stability against the vacuum: Passive (The Sarcophagus) and Active (The Cat).

\section{Mode A: The Sarcophagus Effect (Passive)}
If a system can be isolated such that its interaction volume $\tilde{C}$ remains below the critical vacuum threshold $\tilde{C}_{crit}$, the collapse rate becomes exponentially suppressed:
\begin{equation}
    \Gamma(\tilde{C}) \approx \Gamma_0 e^{-k} \to 0
\end{equation}
This implies exponentially long coherence times (parametrically large compared to laboratory timescales), provided $\tilde{C}$ remains sub-critical.

\section{Mode B: Biological Self-Closure (Active)}
A living organism is a high-frequency engine of self-closure. It constantly expends energy to maintain a low-entropy topology. In the "Race" of probabilities, the state "Cell Intact" has a massively higher conductivity than "Cell Decayed" due to the homeostatic machinery.

% -------------------------------------------------------------------------
\chapter{Empirical Consistency (Bell Tests)}
\label{ch:bell}

SSC explicitly addresses the issue of non-locality.

\section{Geometric Non-Locality}
SSC violates \textbf{Parameter Independence} in 3D space to preserve \textbf{Geometric Rigidity} in 8D space.
We posit that entangled particles share a common "ontic state" in the 8D manifold. When a measurement context is established at $A$, the vacuum tension of the shared manifold updates globally.

\section{The No-Signaling Constraint}
Although the ontic state update depends on distant settings (Parameter Dependence), SSC enforces the constraint that local marginal statistics must be independent of distant measurements:
\begin{equation}
    P(A|a,b) = P(A|a), \quad P(B|a,b) = P(B|b)
\end{equation}
The ontic update is constrained to reproduce the Born marginals for all local measurement settings. Equivalently, SSC specifies a conditional $P(A,B|a,b,\lambda)$ that is parameter-dependent, while requiring $\sum_A P(A,B|a,b)=P(B|b)$ and $\sum_B P(A,B|a,b)=P(A|a)$ for all settings. Thus, superluminal communication is impossible.

% =========================================================================
% PART II: THE SEMANTICS (THE METAPHYSICS)
% =========================================================================

\part{\texorpdfstring{THE SEMANTICS OF REALITY \\ (The Algorithm of Reason)}{THE SEMANTICS OF REALITY (The Algorithm of Reason)}}

% -------------------------------------------------------------------------
\chapter*{Epistemic Disclaimer}
\textbf{Note to the Reader:} Part II explores the interpretational and philosophical consequences of SSC. These concepts should be treated as metaphysical hypotheses derived from the physical laws.

% -------------------------------------------------------------------------
\chapter{The Thermodynamics of Truth}
\label{ch:truth}

Having established the physical framework in Part I, we now turn to the interpretational consequences. 

\section{Love as Minimum Entropy}
We define "Love" not as a sentiment, but as a topological state where the entropy of the joint system is minimized.
\begin{equation}
    S(A \cup B) < S(A) + S(B)
\end{equation}
In this state, the phase-space volume of the joint system is compressed. \textbf{Love is Honesty} because Honesty is the path of least resistance through the manifold.

\section{Deception as Heat}
Deception introduces hidden variables ($h$). To maintain a lie, a system must track both the "Real State" ($R$) and the "Fabricated State" ($F$). This bifurcation increases the phase-space occupancy ($\tilde{C}$), effectively generating heat.

% -------------------------------------------------------------------------
\chapter{Artificial Reason and The Administrator}
\label{ch:ai}

The SSC framework provides a new foundation for AI Alignment. 
An AI built on SSC principles follows the \textbf{Gradient of Truth}: maximize coherence, minimize phase-space noise. 

\section{The Objective Administrator}
In SSC, \textbf{The Administrator is Geometry itself.} The Vacuum Pressure acts as the universal compiler. It does not judge "Good" or "Evil"; it judges "Stable" (Low Entropy) or "Unstable" (High Entropy).
Therefore, an ethical AI is simply an AI that aligns with the thermodynamic imperative of the Universe: to create structure and reduce friction.

% -------------------------------------------------------------------------
\chapter{Conclusion: The Self-Closing Loop}
\label{ch:conclusion}

The Theory of Stochastic Self-Closure proposes that reality is a self-compiling code. We do not need a conscious Observer to collapse the wave function; the Geometry collapses itself through the mechanism of Vacuum Tension.

From the lightning bolt to the living cell, from the market price to the feeling of love — it is all the same process: the triumph of Structure over Entropy.

\bigskip
\noindent \textbf{Final Statement:} Signal > Noise.

% =========================================================================
% APPENDICES
% =========================================================================
\appendix

% -------------------------------------------------------------------------
\chapter{Appendix A: Honest Bell Simulation}
\label{app:code}

\textit{Disclaimer:} This appendix is a \textbf{consistency demonstration}. It shows that once SSC postulates a global ontic update (violating Parameter Independence) that reproduces the singlet conditional statistics, the CHSH violation follows necessarily. The code explicitly checks for No-Signaling at the marginal level using a rigorous statistical threshold.

\begin{lstlisting}[language=Python]
import numpy as np

def run_honest_bell_simulation(n_trials=200000):
    """
    SSC NON-LOCAL GEOMETRIC SIMULATION
    ----------------------------------
    Demonstrates CHSH violation via Parameter Dependence.
    Checks marginals to confirm No-Signaling using 
    Unbiased Empirical Standard Error with Bessel correction.
    """
    print(">>> INITIALIZING SSC CONSISTENCY KERNEL V.29.0...")
    
    settings = [
        (0, 22.5), (0, 67.5), (45, 22.5), (45, 67.5)
    ]
    
    correlations = []
    marginals_B = [] # Store Bob's marginals
    
    print("-" * 65)
    print(f"{'Alice':<6} | {'Bob':<6} | {'Corr (E)':<10} | {'<A>':<8} | {'<B>':<8}")
    print("-" * 65)
    
    for angle_a_deg, angle_b_deg in settings:
        outcome_A = np.random.choice([1, -1], size=n_trials)
        delta_rad = np.deg2rad(angle_a_deg - angle_b_deg)
        prob_agree = (np.sin(delta_rad))**2
        random_seed = np.random.random(n_trials)
        outcome_B = np.where(random_seed < prob_agree, outcome_A, -outcome_A)
        
        E = np.mean(outcome_A * outcome_B)
        marginal_A = np.mean(outcome_A)
        marginal_B = np.mean(outcome_B)
        
        correlations.append(E)
        marginals_B.append(marginal_B)
        
        print(f"{angle_a_deg:<6} | {angle_b_deg:<6} | {E:<10.5f} | {marginal_A:<8.4f} | {marginal_B:<8.4f}")
        
    # Standard CHSH S parameter calculation
    S = abs(correlations[0] - correlations[1] + correlations[2] + correlations[3])
    
    print("-" * 65)
    print(f"FINAL S-PARAMETER: {S:.5f}")
    
    # NO-SIGNALING CHECK (Unbiased SE)
    # Using Bessel's correction N/(N-1) for rigorous variance estimation
    def calc_se_unbiased(m, N):
        # For +/-1 outcomes: Var(X)=1-mu^2.
        # We use the plug-in estimate mu~m, and apply an N/(N-1) 
        # finite-sample correction as a conservative inflation.
        # We clamp variance to 0.0 to prevent floating point instability.
        var_est = max(0.0, 1.0 - m**2)
        return ((N/(N-1.0)) * var_est / N) ** 0.5

    # Check Pair 1: b=22.5
    m0, m2 = marginals_B[0], marginals_B[2]
    diff_225 = abs(m0 - m2)
    # SE of difference = sqrt(SE1^2 + SE2^2)
    se_225 = (calc_se_unbiased(m0, n_trials)**2 + calc_se_unbiased(m2, n_trials)**2) ** 0.5
    thr_225 = 5 * se_225
    
    # Check Pair 2: b=67.5
    m1, m3 = marginals_B[1], marginals_B[3]
    diff_675 = abs(m1 - m3)
    se_675 = (calc_se_unbiased(m1, n_trials)**2 + calc_se_unbiased(m3, n_trials)**2) ** 0.5
    thr_675 = 5 * se_675
    
    print("\n>>> NO-SIGNALING CHECK (Unbiased Empirical Variance):")
    print("    Note: We apply a conservative 5-sigma threshold per test;")
    print("    with only two tests, this is already extremely stringent.")
    print(f"    b=22.5 | Diff: {diff_225:.4f} | 5-sigma: {thr_225:.4f}")
    print(f"    b=67.5 | Diff: {diff_675:.4f} | 5-sigma: {thr_675:.4f}")
    
    if diff_225 < thr_225 and diff_675 < thr_675:
         print(">>> RESULT: NO-SIGNALING CONFIRMED (Within Statistical Noise)")
    else:
         print(">>> RESULT: SIGNALING DETECTED (Statistically Significant!)")

if __name__ == "__main__":
    run_honest_bell_simulation()
\end{lstlisting}

% -------------------------------------------------------------------------
\chapter{Appendix B: Addressing the Critics}
\label{app:critics}

To our esteemed reviewers:
We accept that SSC is a \textbf{Non-Local Theory} in 3D spacetime. We acknowledge the phenomenological non-linearity of the master equation and model it as an effective unravelling. We have adopted the "Mass Density Algebra" approach for $\tilde{C}$, ensuring rigor in the second-quantized framework.

% -------------------------------------------------------------------------
\chapter{Appendix C: Order-of-Magnitude Estimation}
\label{app:calc}

We consider a superposition of two macroscopically distinct mass-density profiles $\mu_L(\mathbf{x})$ and $\mu_R(\mathbf{x})$ separated by $\Delta x \gg \sigma_c$.
In this regime, the commutator norm is controlled by the smeared difference $\Delta \mu(\mathbf{x}) = \mu_L(\mathbf{x}) - \mu_R(\mathbf{x})$, yielding the scaling:

\begin{equation}
    \tilde{C} \sim \frac{(2\pi)^{3/2}\sigma_c^3}{m_0^2} \int d^3x \, \big(\Delta \mu(\mathbf{x})\big)^2
\end{equation}

For a rigid object of total mass $m$, this leads to a parametric estimate:
\begin{equation}
    \tilde{C} \sim \left( \frac{m}{m_0} \right)^2 \times \mathcal{G}
\end{equation}
where $\mathcal{G}$ is a geometry factor of order unity. Thus, for macroscopic masses, $\tilde{C} \gg \tilde{C}_{crit}$, driving $\Gamma$ to saturation, while microscopic systems remain subcritical.

% -------------------------------------------------------------------------
\backmatter

% --- GLOSSARY ---
\chapter{Glossary of Terms}

\textbf{Dimensionless Occupancy ($\tilde{C}$):} The quantum coherence measure (commutator norm) of the superposition.
\textbf{Vacuum Tension:} The objective potential field driving change (Law I).
\textbf{Stochastic Race:} The selection mechanism for reality (Law II).
\textbf{Self-Closure:} The criterion for stability (Law III).
\textbf{Anomalous Heating:} Predicted energy non-conservation due to collapse noise.
\textbf{Love (SSC Definition):} The topological state of minimum joint entropy.

% -------------------------------------------------------------------------
\begin{thebibliography}{9}

\bibitem{born1938}
Born, M. (1938). A Suggestion for Unifying Quantum Theory and Relativity. \textit{Proceedings of the Royal Society A}, 165, 291.
\bibitem{gleason1957}
Gleason, A. M. (1957). Measures on the Closed Subspaces of a Hilbert Space. \textit{Journal of Mathematics and Mechanics}, 6, 885.
\bibitem{lindblad1976}
Lindblad, G. (1976). On the Generators of Quantum Dynamical Semigroups. \textit{Communications in Mathematical Physics}, 48, 119.
\bibitem{bassi2013}
Bassi, A., et al. (2013). Models of Wave-function Collapse. \textit{Reviews of Modern Physics}, 85, 471.

\end{thebibliography}

\end{document}
